Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-17 prop_letter.tex
prop_letter.tex Updating Expectation value...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$. These include the empty projector~$\mathbb{0}$,
the identity projector~$\mathbb{1}$, projectors of the form
$\proj{\phi}$ where $\ket{\phi}$ is a pure quantum state (an element
of a Hilbert space), sums of \emph{orthogonal} projectors $P_0$
and~$P_1$ with $P_0P_1=\mathbb{0}$, and products of \emph{commuting}
projectors $P_0$ and~$P_1$ with $P_0P_1=P_1P_0$. In a well-defined
quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given an observable~$\mathbf{O}$ with spectral decomposition
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ one can define the 
expectation value of that observable as
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.
\end{equation}

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. The collection of intervals used in the
definition of a probability measure must satisfy certain properties
that we explain next.

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and events that are certain (e.g., the event covering the entire
sample space).  For each interval $[\ell,r]$, we also need the
interval $[1-r,1-\ell]$ so that if one interval refers to the
probability of an event, the other refers to the probability of the
event's complement.  For example, if we discover as a result of an
experiment that $\mu(E) = [0.2,0.3]$ for some event~$E$, we may
conclude that $\mu(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the previous naïve way of combining the intervals would
give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
probability interval. Moreover the event $E\cup\overline{E}$ is the
identity event covering the entire space; its probability interval
should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
that the two intervals are correlated: there is more information in
the combined event than in each event separately. In our example, even
though the true probability of $\mu(E)$ can be anywhere in the range
$[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

The similar kind of subtleties happens when we want to define the
expectation value of a random variable. Given a random variable
\begin{equation}
X\left(\omega\right)=\begin{cases}
1 & \textrm{, if }\omega\in E\textrm{ ;}\\
2 & \textrm{, if }\omega\notin E\textrm{ .}
\end{cases}
\end{equation}
If we define its expectation value with respect to the IVPM~$\mu$defined
in the previous paragraph naïvely, it would be\begin{subequations}
\begin{eqnarray}
1\cdot\mu(E)+2\cdot\mu(\overline{E}) & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
 & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
 & = & [1.6,1.9]\,.
\end{eqnarray}
\end{subequations}

@@

@@

@@

\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
  for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and the minimal
  subspace of events $\events'$ containing
  $\left\{ P_{i}\right\} _{i=1}^{N}$, then
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
\end{thm}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }
\newcommand{\rmd}{\mathrm{d}}

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$. These include the empty projector~$\mathbb{0}$,
the identity projector~$\mathbb{1}$, projectors of the form
$\proj{\phi}$ where $\ket{\phi}$ is a pure quantum state (an element
of a Hilbert space), sums of \emph{orthogonal} projectors $P_0$
and~$P_1$ with $P_0P_1=\mathbb{0}$, and products of \emph{commuting}
projectors $P_0$ and~$P_1$ with $P_0P_1=P_1P_0$. In a well-defined
quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given an observable~$\mathbf{O}$ with spectral decomposition
$\mathbf{O}=\sum_{i=1}^{N}\lambda_{i}P_{i}$ one can define the 
expectation value of that observable as
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{N}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
\end{equation}

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\bar{\mu}(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. The collection of intervals used in the
definition of a probability measure must satisfy certain properties
that we explain next.

First, for each interval $[\ell,r]$ we have the natural constraint
$0 \leq \ell \leq r \leq 1$ that guarantees that every element of the
interval can be interpreted as a conventional probability. We also
include $\imposs=[0,0]$ and $\necess=[1,1]$ as limiting intervals to
refer to the probability of impossible events (e.g., the null event)
and events that are certain (e.g., the event covering the entire
sample space).  For each interval $[\ell,r]$, we also need the
interval $[1-r,1-\ell]$ so that if one interval refers to the
probability of an event, the other refers to the probability of the
event's complement.  For example, if we discover as a result of an
experiment that $\bar{\mu}(E) = [0.2,0.3]$ for some event~$E$, we may
conclude that $\bar{\mu}(\overline{E}) = [0.7,0.8]$ for the complement event
$\overline{E}$. In addition to these simple conditions, there are some
subtle conditions on how intervals are combined, which we discuss
next.

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\bar{\mu}(E_1)=[\ell_1,r_1]$ and $\bar{\mu}(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\bar{\mu}(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\bar{\mu}(E_1)=[0.1,0.2]$ and
$\bar{\mu}(E_2)=[0.3,0.4]$ we get $\bar{\mu}(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\bar{\mu}(E)=[0.2,0.3]$ and hence
$\bar{\mu}(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the previous naïve way of combining the intervals would
give $\bar{\mu}(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
probability interval. Moreover the event $E\cup\overline{E}$ is the
identity event covering the entire space; its probability interval
should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
that the two intervals are correlated: there is more information in
the combined event than in each event separately. In our example, even
though the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, can be anywhere in the range
$[0.2,0.3]$ and the true probability of {$\bar{\mu}(\overline{E})$}, $\mu(\overline{E})$, can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\bar{\mu}(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\bar{\mu}(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\bar{\mu}(E)$ or~$\bar{\mu}(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\bar{\mu}(E_1\cup E_2) + \bar{\mu}(E_1\cap E_2) \subseteq \bar{\mu}(E_1) + \bar{\mu}(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\bar{\mu}(E_1\cap E_2) = 0$.

The similar kind of subtleties happens when we want to define the
expectation value of a random variable. Given a random variable
\begin{equation}
X\left(\omega\right)=\begin{cases}
1 & \textrm{, if }\omega\in E\textrm{ ;}\\
2 & \textrm{, if }\omega\notin E\textrm{ .}
\end{cases}
\end{equation}
If we define its expectation value with respect to the IVPM~$\bar{\mu}$defined
in the previous paragraph naïvely, it would be\begin{subequations}
\begin{eqnarray}
 &  & 1\cdot\bar{\mu}(E)+2\cdot\bar{\mu}(\overline{E})\\
 & = & 1\cdot[0.2,0.3]+2\cdot[0.7,0.8]\\
 & = & [1\cdot0.2+2\cdot0.7,1\cdot0.3+2\cdot0.8]\\
 & = & [1.6,1.9]\,.
\end{eqnarray}
\end{subequations}However, if the true probability of {$\bar{\mu}(E)$},
$\mu(E)$, is $0.2$, the expectation value with respect to $\mu$
is 
\begin{equation}
1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.2+2\cdot0.8=1.8\,;
\end{equation}
if the true probability of {$\bar{\mu}(E)$}, $\mu(E)$, is $0.3$,
the expectation value with respect to $\mu$ is
\begin{equation}
1\cdot\mu(E)+2\cdot\mu(\overline{E})=1\cdot0.3+2\cdot0.7=1.7\,.
\end{equation}
No matter what the true probability of {$\bar{\mu}(E)$ is the expectation
value of it never reach $1.6$ and $1.9$ because the }naïve expectation
value with respect to $\bar{\mu}$ combines impossible situation all
together. Since a random variable may have more than two values, the
realistic expectation value called the Choquet integral is much more
complex than the naïve one~\citep{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}.

\begin{definition}\label{def:Choquet}Consider a classical IVPM~$\bar{\mu}$
such that $\mul:\events\rightarrow\left[0,1\right]$ and $\mur:\events\rightarrow\left[0,1\right]$
are the left-end and the right-end of $\bar{\mu}$, respectively,
i.e., $\bar{\mu}\left(E\right)=\left[\mul\left(E\right),\mur\left(E\right)\right]$.
We decompose a random variable~$X$ into step functions, but we separate
the positive and negative terms and write like $\sum_{i=1}^{N^{-}}x_{i}^{-}\mathbf{1}_{E_{i}^{-}}+\sum_{i=1}^{N^{+}}x_{i}^{+}\mathbf{1}_{E_{i}^{+}}$,
where 
\begin{equation}
x_{N^{-}}^{-}\le\ldots\le x_{1}^{-}\le0\le x_{1}^{+}\le\ldots\le x_{N^{+}}^{+}
\end{equation}
 and $\left\{ E_{i}^{-}\right\} _{i=1}^{N^{-}}$ and $\left\{ E_{i}^{+}\right\} _{i=1}^{N^{+}}$
are all disjoint. Let $E_{i}^{s\prime}=\bigcup_{j\ge i}E_{j}^{s}$
and $\Delta\mu^{*}\left(E_{i}^{s\prime}\right)=\mu^{*}\left(E_{i}^{s\prime}\right)-\mu^{*}\left(E_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
Then, the Choquet integral of $X$ with respect to $\bar{\mu}$ is
\begin{equation}
\int X\rmd\bar{\mu}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}x_{i}^{s}\left[\Delta\mul\left(E_{i}^{s\prime}\right),\Delta\mur\left(E_{i}^{s\prime}\right)\right]\,.\label{eq:interval-expectation}
\end{equation}
\end{definition}

The Choquet integral is actually what we desire. Consider the \emph{core}
of $\bar{\mu}$ is the set 
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\set{\pmeas:\events\rightarrow[0,1]}{\forall P\in\events.~\pmeas\left(P\right)\in\bar{\mu}\left(P\right)}\,,
\end{equation}
i.e., the set of real-value probability measure consistent with $\bar{\mu}$.
According to Shapley's theorem~\citep{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
the core of $\bar{\mu}$ is always non-empty, and we have the following
theorem\nb\citep{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.

\begin{thm}\label{thm:Rosenmuller}For every classical IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
and any random variable~$X:\Omega\rightarrow\mathbb{R}$, 
\begin{equation}
\int X\rmd\bar{\mu}=\left[\min_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu,\max_{\mu\in\mathrm{core}\left(\bar{\mu}\right)}\int X\rmd\mu\right]\,.
\end{equation}
\end{thm}

@@

After we defined QIVPM, we can merge the definition of quantum expectation
value~(\ref{eq:quantum-expectation}) and the classical Choquet integral~(\ref{eq:interval-expectation})
to the following definition.

\begin{definition}Consider a QIVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\,,\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\,.
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
Then, the expectation value of $\mathbf{O}$ with respect to $\bar{\mu}$
is defined as
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\,.\label{eq:quantum-interval-expectation}
\end{equation}
\end{definition}

@@

Since Thm.~\ref{thm:Shapley} corresponds to classical Shapley's
theorem, Thm.~\ref{thm:Rosenmuller} has its quantum counterpart.

\begin{thm} Given a Hilbert space $\Hilb$ of dimension~$d\ge3$,
for every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, and an
observable~$\mathbf{O}$ with its spectral decomposition~(\ref{eq:spectrum-decomposition}),
let $\events'$ be the minimal subspace of events containing $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}$,
then 
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}}=\left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\,.\label{eq:quantum-interval-expectation-core}
\end{equation}
\end{thm}

@@
